---
author: Ty Hansen
title: Statistics Student
format:
  classic-cv-pdf: default
cvfooter:
  left: "mr.schochastics.net"
  right: "github.com/schochastics"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Statistics and Data Analytics Student at University of Nebraska-Lincoln
    right: Lincoln, Ne
  - title: Field
    left: Business Analyst Intern
    right: thansen334@gmail.com
  - title: Technical Skills
    left: R, Python, SAS, Excel, Tableau, GitHub
    right: (402) 785-8122
execute:
  echo: false
editor: 
  markdown: 
    wrap: 72
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary

Detail-oriented Business Analyst with strong skills in data analysis and
business intelligence. Experienced in supporting system conversions,
analyzing workflows, and aligning business goals with technical
solutions. Effective communicator and collaborative team member, eager
to apply statistical and analytical skills to drive data- informed
decision making.

# Experience

```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Business Analyst Intern", "Sandhills Global", "Mar. 2025 - Present",
    "Lincoln, NE", c("Collaborated with teams to analyze workflows and support system conversions, ensuring smooth transitions and minimal disruption to operations", "Participated in gathering and evaluating organizational requirements to support improved business practices and decision-making strategies", "Worked closely with departments including IT, sales, and operations to align business goals with technical solutions"),
    "Incoming Software Business Analyst Intern", "DMSi", "May 2026 - Aug. 2026",
    "Omaha, NE", c("Accepted offer for summer 2026 internship")
) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Education

```{r}
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "B.S. Statistics and Data Analytics", "University of Nebraska-Lincoln", "Lincoln, Nebraska", "August 2024-May 2027", c("Relevant Coursework: Statistical Learning, Data Visualization, Regression Analysis", "Dean's List"),
    "A.S. Business", "Aims Community College", "Greeley, Colorado", "Aug. 2023-May 2024", c( "Completed foundational coursework in business analytics")
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")
```
